### 2012-06-15 inst/examples/value_of_information.Rmd
updated plots, deterministic example, summary stats on sims

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
````

@@

@@

``` {r sethiplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

@@

  list(sims = sims, opt = opt, policy_uncertainty = c(policy_g, policy_m, policy_i),
  true_stochasticity = c(true_g, true_m, true_i))
}
````

@@

```{r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

```{r }
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

@@

``` {r biblio, echo=FALSE, results="asis"}
I(print(knitcitations::bibliography(), "html"))
````

>>>>

``` {r  echo=FALSE, cache=FALSE }
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
knitcitations::cleanbib()
cache=FALSE
plotcache=FALSE
````

@@

``` {r not_all_zero}
det <- scenario(0.01, 0.0, 0.0)
````

@@

``` {r sethiplots, cache=cacheplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], g = g$D[,1], m = m$D[,1], gm = gm$D[,1], gi = gi$D[,1], gmi = gmi$D[,1]), id = "stock")
ggplot(policy) + geom_point(aes(stock, stock-x_grid[value], color=variable)) + ylab("escapement") 
ggplot(policy) + geom_smooth(aes(stock, stock-x_grid[value], color=variable))+ ylab("escapement")

@@

  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
}
````

@@

``` {r cache=cache}
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

``` {r cache=cache}
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

``` {r tidy, cache=FALSE}
sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

### Plots

``` {r  onerep, cache=plotcache }
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

This plot summarizes the stock dynamics by visualizing the replicates. Reed's S shown again.

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", cache=plotcache}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario", cache=plotcache}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

````

``` {r fig.cap="the distribution of profits by scenario", cache=plotcache}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

Summary statistics

``` {r, cache=FALSE}
profits[, mean(V1), by=uncertainty]
profits[, sd(V1), by=uncertainty]
````

@@

``` {r biblio, echo=FALSE, results="asis"}
print(knitcitations::bibliography(), "html")
````
